SST_patterns

### 2020-01-29 SST_patterns.Rmd
update

ggplot(data = CMC_dur, aes(x = duration)) +
  geom_histogram(aes(fill = product),  
                       position="identity", alpha=0.6) +
  facet_wrap(~site) +
theme_bw()

>>>>

ggplot(data = CMC_dur, aes(x = duration)) +
  geom_histogram(aes(fill = product),  
                       position = "dodge", alpha=0.6) +
   labs(x = "Duration (Days)", y = "Number of upwelling signals", colour = "Temperature products") +
  facet_wrap(~site) +
theme_bw()
